Towards a Neural Co-Processor Which Restores Dexterity After Stroke: Modeling a Proof-of-Concept

### 2021-12-11 paper/article.tex
Paper progress

>>>>

TODO: table of raw healthy vs lesioned vs recovered vs pct recovered

With each experiment, we track two metrics to characterize the learning progress. First, we
track the task loss, which is an MSE loss that measures the co-processor's ability to restore
movement towards the target trajectory. We characterize that measure in terms of its percent
difference from lesioned and healthy performances.

Second, we measure the degree to which the co-processor's solution successfully
differentiates object classes. We measure the ratio of within-class and total variation,
and compare that to the healthy network. Our separation metric $S$ is defined as:

\begin{equation}
	S = \frac{\sigma_{a}}{\sigma_{w}} - \frac{\sigma_{a,h}}{\sigma_{w,h}}
\end{equation}

where $\sigma$ measures the mean variation, across time, and across all data points in
a given sample. $\sigma_{a}$ is the total variation of a dataset, and $\sigma_{w}$
is the average of the within-class variations. The $h$ indicates the healthy
metric. An $S$ value of 0.0 indicates that the grasps for the various object classes
vary to the same degree as the healthy network.

This metric $S$ allows us to differentiate overall task performance improvement
and the ability of the co-processor to condition the grasp based on visual information.
The structure of the delayed reach-to-grasp task can be learned by the co-processor,
i.e. to hold muscle velocities to 0.0 for the initial part of each trial, without it
also learning to differentiate the various object shapes from the brain observations.
$S$ is our metric for differentiating those two co-processor behaviors.

\subsection{Experiment 1: AIP 75\% lesion}
This experiment measures the effect of a loss of task representation neural
machinery on the ability of the co-processor to succeed. In the non-coadaptive
version of this experiment, the loss of neurons involved in encoding the
visual inputs results in the simulated brain being unable to condition its
grasp for the object shape. Likewise, the co-processor doesn't have sufficient
information to improve performance. The lesioned circuit largely

In the co-adaptive case,

See Fig. \ref{fig:results}.

\subsection{Experiment 2: M1 75\% lesion}
\subsection{Experiment 3: F5 and M1 connectivity lesion}
\subsection{Experiment 4: M1 lesion with pre-recovery}
